Supplementary Material \\ Estimating Correspondences of Deformable Objects ``In-the-wild"

### 2015-11-12 supplementary.tex
Updates from ShareLaTeX

\appendix
\section{Dense Active Appearance Model}
\label{sec:daam}

@@

\section{Patch-based Active Appearance Model}
\label{sec:paam}

@@

\begin{figure}[!t]
\centering
\includegraphics[width=\columnwidth]{Suplementory_Meterial/dense_sample_grid}
\caption{Demonstration of sparse sampling from dense shape.}
\label{fig:sparsesample}
\end{figure}

@@

@@

>>>>

\appendix
\section{Dense Active Appearance Model}
\label{sec:daam}
This section presents 1) detailed description of minimising cost function, 2) intrinsic property analysis of dense AAM and 3) visualisation of fitting dense AAMs on faces and ears.

@@

\section{Patch-based Active Appearance Model}
\label{sec:paam}
This section shows spares annotation of densely corespondent shapes are generated, since patch-based AMM support consistent parse annotation only in section~\ref{sec:sparsesample}. Also, shape model visualisation of build patch-based AMM are shown in section~\ref{sec:paam_sm}, as well as corresponding fitting result visualisation are shown in section~\ref{sec:paam_fittingresults}.

@@

\begin{figure}[!t]
\centering
\includegraphics[width=0.3\columnwidth]{Suplementory_Meterial/dsg}
\caption{Demonstration of sparse sampling from dense shape.}
\label{fig:sparsesample}
\end{figure}

As \emph{step 4} in main paper refers, patch-based AAM are suitable for fitting objects that interior appearance having no structure, in this case e.g. arms. But patch-based AAM require consistent sparse annotation. So a sub-sampling step is need to meet such criteria. As we built dense correspondence between shapes, we only sparsely annotation one shape then rest shapes are sub-sampled automatically since sparse samples are preserved in all shapes by dense correspondent. Figure~\ref{fig:fig:sparsesample} shows sparse annotation (blue dots) on dense mean shape (grid visualisation used for visibility) and exemplar projected samples on other shapes.

@@

Figure~\ref{fig:paam_sm} shows mean shape and corresponding \pm 3 variation on first 4 principle components.

@@

Figure~\ref{fig:paam_fittingresults} demonstrates more fitting results produced by fitting patch-base AAM on arms datasets including MPII, FLIC, Fashion Pose and BBC Pose.
